Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-07-26 main_paper.tex
fixup! Update the basic text for sections 2 and 3 replacing references from residual to wild bootstrap and some other minor changes. NOTE THAT I DID NOT CHANGE THE ALGORITHMS YET. THE LATEST VERSION OF THE ALGORITHMS STILL IS THE ONE AT THE BOOT_RD_GENERAL REPOSITORY. COPY AND PASTE THAT WHEN WE SETTLE ON THE NOTATION AND USE OF I_{h} and I_{b}.

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and a limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD.

@@

Under Assumptions~\ref{A1} through ~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As
is standard in the bootstrap literature, we will assume that the number of
bootstrap replications, $B_{1}$, is large enough that the simulation error can
be ignored. Theorem~\ref{T1} presents the result formally.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} through ~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} through ~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}

>>>>

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodated in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and a limitation should be noted in particular. The confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
and higher order derivatives cases (e.g., Regression Kink Designs).

@@

Under Assumptions~\ref{A1}--\ref{A3} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As
is standard in the bootstrap literature, we will assume that the number of
bootstrap replications, $B_{1}$, is large enough that the simulation error can
be ignored. Theorem~\ref{T1} presents the result formally.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1}--\ref{A3},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1}--\ref{A3},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}
